3-advanced

### 2022-07-09 4-other-features.Rmd
bullet point punctuation

 - \code{spatial_n_keep}: the number of spatial match for each site to keep
 - \code{spatial_dist_max}: the maximum distance allowed for a matched pair
 - \code{temporal_n_highest}: the number of peaks used - 3 in the example above
 - \code{temporal_window}: the length of the interval - 5 in the example above
 - \code{temporal_min_match}: the minimum number of matched peaks for a valid matched pair

>>>>

 - \code{spatial_n_keep}: the number of spatial match for each site to keep;
 - \code{spatial_dist_max}: the maximum distance allowed for a matched pair;
 - \code{temporal_n_highest}: the number of peaks used - 3 in the example above;
 - \code{temporal_window}: the length of the interval - 5 in the example above; and
 - \code{temporal_min_match}: the minimum number of matched peaks for a valid matched pair.
